An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2024-09-30 article.tex
article edits backup (switch computer)

@@

Due to the optional and manual recording of data, steps were taken to remove potentially erronous entries. This process first involved discussions with SWA highlighting possible entry errors. At the end of a season any suspect entries, such as a missing entry of fuel but a vineyard having recorded the use of tractors or the other most common being the use of incorrect units (litres instead of megalitres), would warrant calling individual vineyards to clarify values and logic within the data. Similarly suspicious entries within the data were first described to viticulturalists for scrutiny before being addressed, either through the calling growers for clarification or the removal of an observation from the dataset. The data originally contained only two multiclass variables: year and region. The data originally contained granular readings for similar variables that related to their source, such as water use being divided into river , dam, and pressurised water sources. For this study, these related numeric variables, which included water use, irrigation, and electricity were combined to create multiclass variables, which would illustrated the mixture of types utilised by the grower. This decision was driven by a majority of vineyards utilising one source or a second as a backup, with an overwhelming percentage of water/electricity/irrigation prevailing within a single vineyard. Further details about these variables, their classes and their frequency is available in the Appendix. 

@@

@@

XGBoost (eXtreme Gradient Boosting), described in more detail below (and further in the Appendix), were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoost is a type of machine learning method that constructs and ensemble of decision trees to predict or estimate an output variable (the response) based on a number of input variables. The ensemble, can be used to classify classes or predict a continuous response, depending on the nature of the output variable. They were chosen for this analysis as the data contained a mixture of class and continuous variables. Moreover, XGBoost is unaffected by multicollinearity, and offer high predictive performance for a wide variety of purposes, and are capable of identifying and ranking variables and interactions in order of relative importance \citep{chenXGBoostScalableTree2016}.

@@

Four sets of analyses were conducted. In the first set, two XGBoost models were developed, with operational cost and grape revenue as the response variables. The analysis of operational cost and revenue included all variables in Table \ref{tab:vars}. The second set of analyses focused on identifying relationships between the input variables themselves, creating XGBoost models for each other variable so that every variable would have a measure of its relative importance to every other variable (see Section \ref{sec:importance}). Together these models were used to measure the interrelationships of the ten most important variables in determining operational cost and grape revenue using variable importance. These measures of relative importance were used to illustrate the highly interrelated nature of variables within vineyards. The interaction between variables was depicted through the use of Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between the respective predictor variables and the response (see section \ref{sec:importance}).

@@

The third analysis was an XGBoost tree with Region as the response variable. The difference for this model was that relative variable importance for each variable would be measured for the overall importance in determining region, as opposed to a variable's connection to each region specifically. The fourth analysis focussed on profit (the difference between revenue and operational costs) and year, however these results were not included due to low average loss values and model stability (see Appendix).

@@

XGBoost is an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function to create new decision trees that add to the ensemble, improving its predictive power. The loss function is optimised iteratively to improve upon prior trees. The loss function can be any convex function, allowing gradient descent to traverse the loss space until no substantive improvements can be made via traversal. Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting. This makes XGBoost incredibly versatile and accurate, whilst still being interpretable compared to other machine learning methods.

@@

The Sankey and Chord diagrams were constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Both Chord and Sankey diagrams illustrated variable importance through the size of the bands between two variables. The number at the end of a connection in a Sankey diagram indicates a variable's importance (the number of times it appeared within the ensemble). Sankey and Chord diagrams are presented together; with Sankey diagrams showing the connection of a variable to its ten most important predictor variables and chord diagrams showing the interconnectedness of the ten most prominent variables within its associated Sankey diagram. Chord diagrams formed circles, with variables being connected through their relative importance.

@@

The below sections present each of the analyses conducted within this study. This includes the three analyses for Revenue, Operational Cost and Region, with the fourth and final analysis on profit and yield presented in the appendix.
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
% \newline

@@

In part, yield is sometimes restricted simply through access to water resources. Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel or electricity to pressurise their irrigation systems.

>>>>

TODO: expand the litearture review and premise of the article..
There is growing interest from the wine industry in environmentally sustainable practices in the wine industry, and several recent reviews have called for more data-driven studies to show the economic benefits of such practices. While there is evidence to suggest that environmentally sustainable practices can reduce costs, increase efficiency, and improve the quality of grapes, more research is needed to demonstrate these benefits across different regions and climates (Baiano, 2021; Mariani and Vastola, 2015; Montalvo-Falcón et al., 2023).

The success stories in implementing sustainable strategies in vineyards varies in region, climate, grape variety, and scale (SWA, 2022). The variation shows the amount of difference that can exist between vineyards and their unique challenges, as well as the differences in their viable options. Pressures such as salinity, biosecurity, and water availability change from site to site. The complexity of these environmental interactions has led to the bridging of different research areas such as geology, pedology, hydrology and plant sciences; where the on the ground decisions become governed by these complex physical forces as well as by external pressures such as international market demands, disease pressures and natural disasters (Abad et al., 2021; Cortez et al., 2009; Hall et al., 2011; I. Goodwin, et al., 2009; Kasimati et al., 2022; Oliver et al., 2013; Srivastava and Sadistap, 2018).
Cover crops are an example of a sustainable practice in viticulture in which the area between vine rows is seeded with a crop such as grasses or native vegetation. The primary reason for employing cover crops is to reduce the presence of disease and weeds (Delpuech and Metay, 2018). The benefit of reducing diseases and weeds is especially notable, as there is less cause to utilise heavy machinery for spraying herbicides and fungicides, or for mechanical weeding (Capello et al., 2019). The presence of a cover crop can also help to increase soil water retention, reducing erosion and water runoff in shallow soils, having been shown to mitigate runoff during rain events by over 65% (Capello et al., 2020). However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop (Capello et al., 2019; Delpuech and Metay, 2018; Gosling and Shepherd, 2005; Monteiro and Lopes, 2007). A coverage of only 30% is required to provide protection against erosion, yet increased cover provides the benefits of greater biodiversity at the risk of yield (Delpuech and Metay, 2018).
The reduction of tillage operations through optimising tractor efficiency is another practice that reduces energy use in vineyards, decreasing running costs, as well as reducing soil compaction (Capello et al., 2019). An increase in soil compaction has been shown to increase water runoff (Capello et al., 2020). Runoff is a significant factor as extreme rain events can cause large scale soil deposition, creating further erosion and removing topsoil. It is important that the interaction of events such as erosion have on other considerations such as soil health. 
Soil is an important and ongoing consideration for vineyards and interacts with every other practice in various ways at different time scales. For example, cover crops have been shown to be detrimental for soil health in the short term, giving an initial reduction in soil potassium and phosphorus concentrations and no change in nitrogen levels (Gosling and Shepherd, 2005). Conversely, in longer time frames the presence of a cover crop can induce an increase in microorganisms, which can excrete phosphates and potassium, regenerating the soils chemical balance and helping to introduce further organic nitrogen (Coll et al., 2011). The studies that showed this were based in two different countries of similar climate but could have been subject to other underlying conditions not measured. 
When implementing practices such as cover crops the extent of the practice, the compounding effects and potential alternatives need to also be considered. Alternative options are always available such the use of mulch and wood chips to increase soil health and water retention in place of more involved processes such as crop rotation (Rössert et al., 2022). Crop rotation offers greater benefits than other soil management plans (Brock et al., 2011), however this is often not a viable option for many vineyards although is common practice in some places (Russo et al., 2021). The need to look at the holistic outcomes and interactions of these practices is paramount, however with the existence of many different practices, the outcomes due to interactions are not always known; one such consideration is the use of fungicide and its potential to build up copper, causing a reduction of microorganisms in the soil. Linking copper build up to any particular cause is a difficult endeavour due to the need for multiple reliable soil samples which are equally effected by the same conditions, within soil (Wightwick et al., 2010).

@@

Due to the optional and manual recording of data, steps were taken to remove potentially erronous entries. This process first involved discussions with SWA highlighting possible entry errors. At the end of a season any suspect entries, such as a missing entry of fuel but a vineyard having recorded the use of tractors or the other most common being the use of incorrect units (litres instead of megalitres), would warrant calling individual vineyards to clarify values and logic within the data. Similarly suspicious entries within the data were first described to viticulturalists for scrutiny before being addressed, either through the calling growers for clarification or the removal of an observation from the dataset after consulting viticulturalists as to its plausability. Several entries were removed from the study due to impossible recordings such as no fuel of any kind being consumed when tractors were used, or no electricity being used when the irrigation system was electric (most of these were able to be clarified through contacting vineyard owners). 
Due to the nature of XGBoost the data was not needed to be transformed for the algorithms consumption with the exception of multiclass variables being converted to one-hot-encoded variables, with the data originally containing only two multiclass variables: year and region. Only two augmenetations were done to the data for this analysis beyond data cleaning, the first was to convert the continuous variables (fuel, electricity, water, yield, etc) into ratio's of a vineyard to reflect the consumption of resources and output yield per hectare to compare the outputs to non-transformed models.

The second transfomration, was done to add clarity in interpretting the relative importance scores. Where, variables that related to the source of a resource, such as water use being divided into river, dam, and pressurised water sources were summed into total electricity/water variables. The source of these (such as river, dam, pressurised water) were converted into binary variables that reflected the presence of a source being used. Other potentially multi-class variables such as irrigation and cover crops were also converted to reflect whether a grower simply used these types of systems as opposed to the dict amount of area covered by them. This decision was driven by a majority of vineyards utilising one source or a second as a backup, with an overwhelming percentage of water/electricity/irrigation prevailing within a single vineyard. The use of a binarisation also meant that importance measures would be better understood as they forced ensemble to partition by presence or absence of a type of system as opposed to a potentially overly specific number. This further helps to relate relative importance values for these variables directly to the importance of using a system over another. This approach was also used after finding little difference in model accuracy between whether these variables were reported as proportion of a type used (i.e the percentage of land covered by drip irrigation), direct units of a type (i.e M\\L river water used) or as a binary presence/absence. Further details about these variables, their classes and their frequency is available in the Appendix.

@@

TODO: talk about external climatic data

@@

XGBoost (eXtreme Gradient Boosting) is an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function to create new decision trees that add to the ensemble, improving its predictive power. The loss function is optimised iteratively to improve upon prior trees (where the loss function can be any convex function), allowing gradient descent to traverse the loss space until no substantive improvements can be made (detail pertaining to the algorithm is described further in the Appendix). Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting. This makes XGBoost incredibly versatile and accurate, whilst still being interpretable compared to other machine learning methods (TODO: ref).
XGBoost analyses were conducted using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. It is a method that is widely used within agriculture for yield prediction (TODO: ref), but is also highly capable method for financial predictions, even when dealing with multi-domain predictor variables (TODO: ref). We utilise XGBoot due to a combination of agricultural yield prediction, financial prediction and the use of both economic and environmental variables where it is known to perform well with mixed types of predictor domains (TODO: ref). Furthermore we choose XGBoost as it has a good performance in predictions whislt allowing the use of directly comparable metrics to sanity check models against prior research (such as yield using $R^2$), offering insight into the relative performance of models lacking prior reference points in the literature such as revenue and operating costs and making the model more interpretable to audiences familiar with regression models. 

@@

The ability to classify and predict continuous response variables and categoric variables alongside one another was also a consideration in the use of XGBoost, as both were contained in the data. XGBoost was also used due to its ability to handle sparse data, which was present within this dataset due to the voluntary nature of data entry, with many fields being left blank during data collection. Tree based methods also do not require data to be transformed prior to analyses; this consideration was taken into account so that specific partitions of values could be evaluated more easily and understood within original units of the data (TODO: ref). A further consideration in its use was the level of interpretability offered through measures of 'relative importance' allowing for the ability to identify and rank variables and interactions by contribution to predictions \citep{chenXGBoostScalableTree2016}.

@@

An XGBoost model was trained for each variable so that every variable's relative importance could be caculated. This process was done three time using three iterations of data (three models for each variable). The first models were trained on the original SWA data set, the second were trained on a dataset that incorporated external data for each region (see TODO: insert a table for this) and the final were trained on data with continuous variables  transformed to be expressed as a ratio of vineyard area. The final dataset that consisted of ratios also included the extra regional data (but not in ratio form).

@@

\subsection{Sankey and Chord Diagrams}
Originally created by Sankey to depict different pressures in steam engines (TODO: ref) we leverage Sankey diagrams to illustrate the different impact or 'pressure' each variable has on one another through the use of measurements of variable importance. Sankey and Chord diagrams were constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Sankey diagrams (depicted on the left as section Asection A in figures) show the top 10 contributing factors to a variables prediction using XGBoost and Chord diagrams, a circular represntation of Sankey diagrams (depicted on the right as section B in figures) show how each of the top 10 factors relate to one another by measures of relative importance.
Both Chord and Sankey diagrams illustrate variable importance through the size of the bands between two variables. The number at the end of a connection in the diagrams indicates a variabless importance (the number of times it appeared within the ensemble).

@@

@@

% The below sections present each of the analyses conducted within this study. This includes the three analyses for Revenue, Operational Cost and Region, with the fourth and final analysis on profit and yield presented in the appendix.
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
% \newline

@@

In part, yield is sometimes restricted simply through access to water resources. Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region due to vineyards in regions without pressurised water needing to use fuel or electricity to pressurise their irrigation systems. Although infrastructure between regions, especially further from cities is likely to vary, fuel price itself has little variation across regional Australia. It is reported by the Australian Competition and Consumer Commission that during the period of this data, that regional fuel prices tended to be higher (+5.4c/litre) and more stable than urban prices due to their primary driver being international market trends~\citep{aipFactsPricesRegional2019}. The importance between fuel and other variables is a complicated interaction. The size, number of blocks, types and age of equipment will contribute to the efficiency of its use and the amount required across a site. It is likely that larger operations will generaly gain from economies of scale but also risk further incurring costs from the need to redeploy equipment. A further connection between region and fuel is the possible requirement of more specialty equipment, either due to regional practices differing or physical requirements such as greater inclines. However, the style of management will also greatly contribute to how efficient both fuel and water are used, which is difficult to account for through the use of a metric.
